---
title: "Assignment 3 - Causal inference"
author: "Group 6: Nanna, Helene, Katrine, Bianka R and Stine F.H."
date: "2/5/2020"
output: 
  md_document:
    variant: markdown_github
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Assignment 3 - Exploring causal inference issues

In this assignment we explore some issues related to multiple regressions (regressions with more than one predictor), and inferred (causal) relations between variables. N.B. the data is simulated (to make sure I know the actual mechanism generating it), but it's based on a real study. So bear with a longish introduction to get into the details of what we are doing and why it is important.

### Altercentric intrusion in schizophrenia

People with schizophrenia often report altered control and distinction of self-other representations: intrusive thoughts, hearing of voices, delusions of mind reading, paranoia, etc (a substantial portion of the psychotic symptoms experienced in schizophrenia). These have been variously attributed to hypermentalizing (over attribution of mental states to others), social impairment (over preoccupation with own thought processes), hyper socialization (inability to inhibit information from others), etc.

The current study investigates 1) whether schizophrenia is indeed related to altered control and distinction of self-other representations, in particular altercentric intrusions (inability to inhibit social information), and 2) whether these are related to the relevant psychotic symptoms. N.B. the actual study also investigates egocentric intrusion, do check the papers below if interested.

The task is a slightly modified version of this: https://www.ncbi.nlm.nih.gov/pubmed/20731512 
- Some dots visible to you
- Different person with a different set of dots visible to them. 
- Can be(congruent condition) or not (incongruent condition). 
- You are tasked to indicate whether a given number (e.g. 3) matches the number of dots you see (and the dots visible to the other person are irrelevant to the task).


The tasks investigates altercentric intrusion 
--> Will your RT change according to whether the other person is seeing the same amount of dots as you, or not? 

So RT in relation to congruent vs. incongruent trials. 
So for longer RT in incongruent trials --> the bigger the altercentric intrusion effect 

The idea is that if you correctly inhibit social information, your reaction time should not change, as the information about the other person is not relevant. On the contrary, if you nevertheless use task irrelevant social information, you'll be slower at indicating whether 3 is the right number of dots when the other person sees a different amount of dots than you (conflicting information).
The bigger the difference between RTs in the congruent and incongruent condition the bigger the altercentric intrusion effect.

For each participant you have 6 variables: 
1) ID, 
2) AltercentricIntrusion (continuous score), 
3) Diagnosis (schizophrenia vs. control), 
4) VoiceHearing (severity of voice hearing symptoms, continuous score of the severity of the symptom as measured by a clinician), 
5) MindReading (severity of delusions of mind reading, continuous score of the severity of the symptom as measured by a clinician); 
6) Apathy (severity of lack of motivation in taking care of oneself, from washing to showing up at work, continuous score of the severity of the symptom as measured by a clinician).

The research questions you have to answer are the following:

## First part

Q1.1) Does schizophrenia involve altercentric intrusion? 
Define model and priors. 
Test the implications of your priors (prior predictive checks) and if needed adjust them. Run the model. 
Test the quality of the fitted model (posterior predictive checks). 
Assess the evidence in favor of an increased altercentric intrusion in schizophrenia. Report the model and the results, including plots.

```{r}
pacman::p_load(tidyverse, brms)

# Prepare the data
setwd("~/Cognitive Science/4th semester/Computational modeling/R code/4sem_ass3")
d <- read_csv("Ass3.csv")
#summary(d)

# We rename diagnosis varable
d$Diagnosis <- plyr::revalue(as.character(d$Diagnosis), 
                             c("0"="Controls", "1"="Schizophrenia")) 
# We make into factors
d <- d %>%
  mutate(
    ID = as.factor(ID),
    Diagnosis = as.factor(Diagnosis)
  )

# Define the formula with bf

# With an intercept
AltercentricDiagnosis_f0 <- bf(
  AltercentricIntrusion ~ 1 + Diagnosis
)

# We look at the preditors different from 0 so no intercept
AltercentricDiagnosis_f <- bf(
  AltercentricIntrusion ~ 0 + Diagnosis
)

# Design the priors

# We look at the default priors
get_prior(AltercentricDiagnosis_f0, family = gaussian, d)
get_prior(AltercentricDiagnosis_f, family = gaussian, d)

# We make our own priors
priorDiagnosis <- c(
  prior(normal(4, 1), class = b),
  prior(normal(1, 2), class = sigma) # 2 then makes it possible to error up to 5
) 

# Test the priors

AltercentricDiagnosis_PriorCheck_m <- brm(
  formula = AltercentricDiagnosis_f,
  data = d,
  family = gaussian,
  prior = priorDiagnosis,
  sample_prior = "only", #Only looks at priors
  file = "AltercentricDiagnosis_PC"
)

#Prior predictive check
pp_check(AltercentricDiagnosis_PriorCheck_m, nsamples = 100) # Are the generated values in the right magnitude?
# It looks fine

## Fitting the model
AltercentricDiagnosis_m <- brm(
  formula = AltercentricDiagnosis_f,
  data = d,
  family = gaussian,
  prior = priorDiagnosis,
  sample_prior = T,
  file = "AltercentricDiagnosis"
)
AltercentricDiagnosis_m 
# Posterior predictive check
pp_check(AltercentricDiagnosis_m, nsamples = 100)
# "the data looks fantastic" - Riccardo Fusaroli

## Check the model for warnings
AltercentricDiagnosis_m

#Has the posterior learned from the data? Less uncertain than prior predictive check
# Hypothesis testing + updating check
plot(hypothesis(AltercentricDiagnosis_m,
           "DiagnosisSchizophrenia > DiagnosisControls"))

hypothesis(AltercentricDiagnosis_m,
           "DiagnosisSchizophrenia > DiagnosisControls")
# the beta value indicates a difference, and by looking at the error and confidence intervals we see that it is likely that this difference is "true". 

conditional_effects(AltercentricDiagnosis_m)

# The participants level of altercentric intrusion vs. model's estimate.
plot(conditional_effects(AltercentricDiagnosis_m), points=T)

```

The model indicates a credible difference in altercentric intrusion in the two groups supporting our hypothesis (b = 0.36, CIs = 0.16, 0.57, ER = 1332). 

Controls showed on average an altercentric intrusion effect of 3.86 (CIs 3.74, 3.98), and schizophrenia of 4.22 (CIs = 4.01, 4.43).

[Add plot of the effects]

# SI
The model had no divergences, a Rhat of 1, and Effective Sample Sizes above 2000 for both Bulk and Tail.
[Add prior and posterior checks plots; add updating check plot]

Q1.2) Is altercentric intrusion related to specific symptoms *in the patients*? 
Identify which of the symptoms could be relevant. Should you include more than one symptom? 
Build models, priors, predictive checks. Assess the evidence and report models and results, including plots. 
Discuss whether the results make sense.


We should subset the data to only contrain scitzophrenics because we usually never get data for symptoms of controls

If we don't scale there are pretty heavy correlations between intercept and slope
```{r}
# We scale the data
d <- d %>% 
  mutate(
  AltercentricIntrusion = scale(AltercentricIntrusion),
  VoiceHearing = scale(VoiceHearing),
  MindReading = scale(MindReading),
  Apathy = scale(Apathy)
)

# We subset the data
d <- d %>% subset(Diagnosis == "Schizophrenia")
```


For VoiceHearing
```{r}
#Predict altercentric intrusion from the other symptoms. 

# Does VoiceHearing predict altercentric intrusion
# We make a model for each of the symptoms

# Define the formula with bf

# With a continous predictor we want an intercept in the model

# We look at the preditors different from 0 so no intercept
AltercentricVH<- bf(
  AltercentricIntrusion ~ 1 + VoiceHearing
)

# Design the priors

# We look at the default priors
get_prior(AltercentricVH, family = gaussian, d)

# We make our own priors
priorVH <- c(
  prior(normal(0, 1), class = Intercept),
  prior(normal(0, .3), class = b),
  prior(normal(1, 2), class = sigma) 
) 

# Test the priors

AltercentricVH_PriorCheck_m <- brm(
  formula = AltercentricVH,
  data = d,
  family = gaussian,
  prior = priorVH,
  sample_prior = "only", #Only looks at priors
  file = "AltercentricVoiceHearing_PC_1"
)

#Prior predictive check
pp_check(AltercentricVH_PriorCheck_m, nsamples = 100) # Are the generated values in the right magnitude?
# It looks fine


## Fitting the model
AltercentricVH_m <- brm(
  formula = AltercentricVH,
  data = d,
  family = gaussian,
  prior = priorVH,
  sample_prior = T,
  file = "AltercentricVoiceHearing"
)

pp_check(AltercentricVH_m, nsamples = 100)
# 

conditional_effects(AltercentricVH_m)

# The participants level of altercentric intrusion vs. model's estimate.
plot(conditional_effects(AltercentricVH_m), points=T)

# Hypothesis testing
hypothesis(AltercentricVH_m,
           "VoiceHearing > 0")

# 0.05, evid ratio 2.3
```
For Mind-Reading
```{r}
# We look at the preditors different from 0 so no intercept
AltercentricMR<- bf(
  AltercentricIntrusion ~ 1 + MindReading
)

# Design the priors

# We look at the default priors
get_prior(AltercentricMR, family = gaussian, d)

# We make our own priors
priorMR <- c(
  prior(normal(0, 1), class = Intercept),
  prior(normal(0, 0.3), class = b),
  prior(normal(1, 2), class = sigma) # 2 then makes it possible to error up to 5
) 

# Test the priors

AltercentricMR_PriorCheck_m <- brm(
  formula = AltercentricMR,
  data = d,
  family = gaussian,
  prior = priorMR,
  sample_prior = "only", #Only looks at priors
  file = "AltercentricMR_PC"
)

#Prior predictive check
pp_check(AltercentricMR_PriorCheck_m, nsamples = 100) # Are the generated values in the right magnitude?
# It looks fine

## Fitting the model
AltercentricMR_m <- brm(
  formula = AltercentricMR,
  data = d,
  family = gaussian,
  prior = priorVH,
  sample_prior = T,
  file = "AltercentricMR"
)


pp_check(AltercentricMR_m, nsamples = 100)

conditional_effects(AltercentricMR_m)

# The participants level of altercentric intrusion vs. model's estimate.
plot(conditional_effects(AltercentricMR_m), points=T)

# Hypothesis testing
hypothesis(AltercentricMR_m,
           "MindReading > 0")

# Estimate 0.08, evid ratio 3.1
```

For Apathy
```{r}
# We look at the preditors different from 0 so no intercept
AltercentricA<- bf(
  AltercentricIntrusion ~ 1 + Apathy
)

# Design the priors

# We look at the default priors
get_prior(AltercentricA, family = gaussian, d)

# We make our own priors
priorA <- c(
  prior(normal(0, 1), class = Intercept),
  prior(normal(0, 0.3), class = b),
  prior(normal(1, 2), class = sigma) # 2 then makes it possible to error up to 5
) 

# Test the priors

AltercentricA_PriorCheck_m <- brm(
  formula = AltercentricA,
  data = d,
  family = gaussian,
  prior = priorA,
  sample_prior = "only", #Only looks at priors
  file = "AltercentricA_PC"
)

#Prior predictive check
pp_check(AltercentricA_PriorCheck_m, nsamples = 100) # Are the generated values in the right magnitude?
# It looks fine

## Fitting the model
AltercentricA_m <- brm(
  formula = AltercentricA,
  data = d,
  family = gaussian,
  prior = priorA,
  sample_prior = T,
  file = "AltercentricA"
)

AltercentricA_m

pp_check(AltercentricA_m, nsamples = 100)
# 

conditional_effects(AltercentricA_m)

# The participants level of altercentric intrusion vs. model's estimate.
plot(conditional_effects(AltercentricA_m), points=T)

# Hypothesis testing
hypothesis(AltercentricA_m,
           "Apathy < 0")

# 

```
Together in a multilevel model
```{r}
# We make the formula
AltercentricMRVH <- bf(
  AltercentricIntrusion ~ 1 + VoiceHearing + MindReading
)

# Design the priors

# We look at the default priors
get_prior(AltercentricMRVH, family = gaussian, d)

# We make our own priors
priorMRVH <- c(
  prior(normal(0, 1), class = Intercept),
  prior(normal(0, 0.3), class = b),
  prior(normal(1, 2), class = sigma) # 2 then makes it possible to error up to 5
) 

# Test the priors

AltercentricMRVH_PriorCheck_m <- brm(
  formula = AltercentricMRVH,
  data = d,
  family = gaussian,
  prior = priorMRVH,
  sample_prior = "only", #Only looks at priors
  file = "AltercentricMRVH_PC"
)

#Prior predictive check
pp_check(AltercentricMRVH_PriorCheck_m, nsamples = 100) # Are the generated values in the right magnitude?
# It looks fine

## Fitting the model
AltercentricMRVH_m <- brm(
  formula = AltercentricMRVH,
  data = d,
  family = gaussian,
  prior = priorMRVH,
  sample_prior = T, 
  file = "AltercentricMRVH"
)
AltercentricMRVH_m
pp_check(AltercentricMRVH_m, nsamples = 100)


stanplot(AltercentricMRVH_m)

# Hypothesis testing
hypothesis(AltercentricMRVH_m,
           "MindReading > 0")
hypothesis(AltercentricMRVH_m,
           "VoiceHearing > 0")

# Estimate 0.04, evid 1.85

```
Multilevel model with all predictors
```{r}
# We make the formula
AltercentricMRVHA <- bf(
  AltercentricIntrusion ~ 1 + MindReading + VoiceHearing + Apathy
)

# Design the priors

# We look at the default priors
get_prior(AltercentricMRVHA, family = gaussian, d)

# We make our own priors
priorMRVHA <- c(
  prior(normal(0, 1), class = Intercept),
  prior(normal(0, 0.3), class = b),
  prior(normal(1, 2), class = sigma) # 2 then makes it possible to error up to 5
) 

# Test the priors

AltercentricMRVHA_PriorCheck <- brm(
  formula = AltercentricMRVHA,
  data = d,
  family = gaussian,
  prior = priorMRVHA,
  sample_prior = "only", #Only looks at priors
  file = "AltercentricMRVHA_PC"
)

#Prior predictive check
pp_check(AltercentricMRVHA_PriorCheck, nsamples = 100) # Are the generated values in the right magnitude?
# It looks fine

## Fitting the model
AltercentricMRVHA_m <- brm(
  formula = AltercentricMRVHA,
  data = d,
  family = gaussian,
  prior = priorMRVHA,
  sample_prior = T, 
  file = "AltercentricMRVHA"
)

pp_check(AltercentricMRVHA_m, nsamples = 100)

# Hypothesis testing
hypothesis(AltercentricMRVHA_m,
           "Apathy > 0")

# Estimate 

```

We can do model comparison
```{r}
AltercentricVH_c <- add_criterion(AltercentricVH_m, criterion = "loo")
AltercentricMR_c <- add_criterion(AltercentricMR_m, criterion = "loo")
AltercentricA_c <- add_criterion(AltercentricA_m, criterion = "loo")
AltercentricMRVH_c <- add_criterion(AltercentricMRVH_m, criterion = "loo")
AltercentricMRVHA_c <- add_criterion(AltercentricMRVHA_m, criterion = "loo")

loo_compare(AltercentricVH_c, 
               AltercentricMR_c, 
               AltercentricA_c, 
               AltercentricMRVH_c, 
               AltercentricMRVHA_c)

loo_model_weights(AltercentricVH_c, 
               AltercentricMR_c, 
               AltercentricA_c, 
               AltercentricMRVH_c, 
               AltercentricMRVHA_c)
```
We expect VH and MR to be related to AI but not Apathy
A model comparison approach predicting AI from apathy is the best model minimizing estimated out of sample error stacking weight of 1. Adding other symptoms does not improve generalizability of the model. 



## Second part

Q2.1) However, we know that the diagnosis is based on symptom assessment: if the overall sum of symptoms is severe enough, the participant gets a diagnosis. In other words, by selecting the patients, and including the symptoms in the model we might have inadvertently introduced an issue in our inference. Do try to draw a causal graph (Directed Acyclical Graph) of the variables and compare it with the types of causal graphs presented in the slides. Discuss which biases you might have introduced.


Q2.2.) Redesign your analysis following the graph and report how the results change
```{r}
# Prepare the data
d <- read_csv("Ass3.csv")
#summary(d)

# We scale the data
d <- d %>% 
  mutate(
  AltercentricIntrusion = scale(AltercentricIntrusion),
  VoiceHearing = scale(VoiceHearing),
  MindReading = scale(MindReading),
  Apathy = scale(Apathy)
)
```


For VoiceHearing
```{r}
#Predict altercentric intrusion from the other symptoms. 

# Does VoiceHearing predict altercentric intrusion
# We make a model for each of the symptoms

# Define the formula with bf

# With a continous predictor we want an intercept in the model

# We look at the preditors different from 0 so no intercept
AltercentricVH<- bf(
  AltercentricIntrusion ~ 1 + VoiceHearing
)

# Design the priors

# We look at the default priors
get_prior(AltercentricVH, family = gaussian, d)

# We make our own priors
priorVH <- c(
  prior(normal(0, 1), class = Intercept),
  prior(normal(0, .3), class = b),
  prior(normal(1, 2), class = sigma) 
) 

# Test the priors

AltercentricVH_PriorCheck_m <- brm(
  formula = AltercentricVH,
  data = d,
  family = gaussian,
  prior = priorVH,
  sample_prior = "only", #Only looks at priors
  file = "All_AltercentricVoiceHearing_PC_1"
)

#Prior predictive check
pp_check(AltercentricVH_PriorCheck_m, nsamples = 100) # Are the generated values in the right magnitude?
# It looks fine


## Fitting the model
AltercentricVH_m <- brm(
  formula = AltercentricVH,
  data = d,
  family = gaussian,
  prior = priorVH,
  sample_prior = T,
  file = "All_AltercentricVoiceHearing"
)

pp_check(AltercentricVH_m, nsamples = 100)
# 

conditional_effects(AltercentricVH_m)

# The participants level of altercentric intrusion vs. model's estimate.
plot(conditional_effects(AltercentricVH_m), points=T)

# Hypothesis testing
hypothesis(AltercentricVH_m,
           "VoiceHearing > 0")
```
For Mind-Reading
```{r}
# We look at the preditors different from 0 so no intercept
AltercentricMR<- bf(
  AltercentricIntrusion ~ 1 + MindReading
)

# Design the priors

# We look at the default priors
get_prior(AltercentricMR, family = gaussian, d)

# We make our own priors
priorMR <- c(
  prior(normal(0, 1), class = Intercept),
  prior(normal(0, 0.3), class = b),
  prior(normal(1, 2), class = sigma) # 2 then makes it possible to error up to 5
) 

# Test the priors

AltercentricMR_PriorCheck_m <- brm(
  formula = AltercentricMR,
  data = d,
  family = gaussian,
  prior = priorMR,
  sample_prior = "only", #Only looks at priors
  file = "All_AltercentricMR_PC"
)

#Prior predictive check
pp_check(AltercentricMR_PriorCheck_m, nsamples = 100) # Are the generated values in the right magnitude?
# It looks fine

## Fitting the model
AltercentricMR_m <- brm(
  formula = AltercentricMR,
  data = d,
  family = gaussian,
  prior = priorVH,
  sample_prior = T,
  file = "All_AltercentricMR"
)


pp_check(AltercentricMR_m, nsamples = 100)

conditional_effects(AltercentricMR_m)

# The participants level of altercentric intrusion vs. model's estimate.
plot(conditional_effects(AltercentricMR_m), points=T)

# Hypothesis testing
hypothesis(AltercentricMR_m,
           "MindReading > 0")


```

For Apathy
```{r}
# We look at the preditors different from 0 so no intercept
AltercentricA<- bf(
  AltercentricIntrusion ~ 1 + Apathy
)

# Design the priors

# We look at the default priors
get_prior(AltercentricA, family = gaussian, d)

# We make our own priors
priorA <- c(
  prior(normal(0, 1), class = Intercept),
  prior(normal(0, 0.3), class = b),
  prior(normal(1, 2), class = sigma) # 2 then makes it possible to error up to 5
) 

# Test the priors

AltercentricA_PriorCheck_m <- brm(
  formula = AltercentricA,
  data = d,
  family = gaussian,
  prior = priorA,
  sample_prior = "only", #Only looks at priors
  file = "All_AltercentricA_PC"
)

#Prior predictive check
pp_check(AltercentricA_PriorCheck_m, nsamples = 100) # Are the generated values in the right magnitude?
# It looks fine

## Fitting the model
AltercentricA_m <- brm(
  formula = AltercentricA,
  data = d,
  family = gaussian,
  prior = priorA,
  sample_prior = T,
  file = "All_AltercentricA"
)

AltercentricA_m

pp_check(AltercentricA_m, nsamples = 100)
# 

conditional_effects(AltercentricA_m)

# The participants level of altercentric intrusion vs. model's estimate.
plot(conditional_effects(AltercentricA_m), points=T)

# Hypothesis testing
hypothesis(AltercentricA_m,
           "Apathy < 0")

# 

```
Together in a multilevel model
```{r}
# We make the formula
AltercentricMRVH <- bf(
  AltercentricIntrusion ~ 1 + VoiceHearing + MindReading
)

# Design the priors

# We look at the default priors
get_prior(AltercentricMRVH, family = gaussian, d)

# We make our own priors
priorMRVH <- c(
  prior(normal(0, 1), class = Intercept),
  prior(normal(0, 0.3), class = b),
  prior(normal(1, 2), class = sigma) # 2 then makes it possible to error up to 5
) 

# Test the priors

AltercentricMRVH_PriorCheck_m <- brm(
  formula = AltercentricMRVH,
  data = d,
  family = gaussian,
  prior = priorMRVH,
  sample_prior = "only", #Only looks at priors
  file = "All_AltercentricMRVH_PC"
)

#Prior predictive check
pp_check(AltercentricMRVH_PriorCheck_m, nsamples = 100) # Are the generated values in the right magnitude?
# It looks fine

## Fitting the model
AltercentricMRVH_m <- brm(
  formula = AltercentricMRVH,
  data = d,
  family = gaussian,
  prior = priorMRVH,
  sample_prior = T, 
  file = "All_AltercentricMRVH"
)
AltercentricMRVH_m
pp_check(AltercentricMRVH_m, nsamples = 100)


stanplot(AltercentricMRVH_m)

# Hypothesis testing
hypothesis(AltercentricMRVH_m,
           "MindReading > 0")
hypothesis(AltercentricMRVH_m,
           "VoiceHearing > 0")
# We plot them
plot(hypothesis(AltercentricMRVH_m,
           "MindReading > 0"))
plot(hypothesis(AltercentricMRVH_m,
           "VoiceHearing > 0"))

```
Multilevel model with all predictors
```{r}
# We make the formula
AltercentricMRVHA <- bf(
  AltercentricIntrusion ~ 1 + MindReading + VoiceHearing + Apathy
)

# Design the priors

# We look at the default priors
get_prior(AltercentricMRVHA, family = gaussian, d)

# We make our own priors
priorMRVHA <- c(
  prior(normal(0, 1), class = Intercept),
  prior(normal(0, 0.3), class = b),
  prior(normal(1, 2), class = sigma) # 2 then makes it possible to error up to 5
) 

# Test the priors

AltercentricMRVHA_PriorCheck <- brm(
  formula = AltercentricMRVHA,
  data = d,
  family = gaussian,
  prior = priorMRVHA,
  sample_prior = "only", #Only looks at priors
  file = "All_AltercentricMRVHA_PC"
)

#Prior predictive check
pp_check(AltercentricMRVHA_PriorCheck, nsamples = 100) # Are the generated values in the right magnitude?
# It looks fine

## Fitting the model
AltercentricMRVHA_m <- brm(
  formula = AltercentricMRVHA,
  data = d,
  family = gaussian,
  prior = priorMRVHA,
  sample_prior = T, 
  file = "All_AltercentricMRVHA"
)

AltercentricMRVHA_m
pp_check(AltercentricMRVHA_m, nsamples = 100)

# Hypothesis testing
plot(hypothesis(AltercentricMRVHA_m,
           "Apathy > 0"))

# Estimate 

```

We can do model comparison
```{r}
AltercentricVH_c <- add_criterion(AltercentricVH_m, criterion = "loo")
AltercentricMR_c <- add_criterion(AltercentricMR_m, criterion = "loo")
AltercentricA_c <- add_criterion(AltercentricA_m, criterion = "loo")
AltercentricMRVH_c <- add_criterion(AltercentricMRVH_m, criterion = "loo")
AltercentricMRVHA_c <- add_criterion(AltercentricMRVHA_m, criterion = "loo")

loo_compare(AltercentricVH_c, 
               AltercentricMR_c, 
               AltercentricA_c, 
               AltercentricMRVH_c, 
               AltercentricMRVHA_c)

loo_model_weights(AltercentricVH_c, 
               AltercentricMR_c, 
               AltercentricA_c, 
               AltercentricMRVH_c, 
               AltercentricMRVHA_c)
``` 
